A smart street lighting system based on \rev{an} IPv6-enabled wireless sensor network

### 2014-11-26 2014_ELSEVIER_CEE_SI/paper_cee_special_issue.tex
correção das aspas

\rev{With  the increase in world population and the growing urbanization worldwide, cities will need to evolve towards an intelligent infrastructure in order to provide to its citizens a better living environment. This will be achieved through the use of information and communication technology (ICT), with the goal to provide public services that are more accessible and more efficient. This vision is embodied in the "smart city" concept. \refs{(A Smart City and the Applications, 2011, Global Perspective of Smart Cities: A Survey, 2013).}}

\rev{According to several researchers, to enable the smart city it will be required an urban "Internet of Things(IoT)" infrastructure, where sensors and actuators distributed across the city will be interconnected by a pervasive network. \refs{(Developing an IoT Smart City Framework, Internet of Things for Smart Cities, An Information Framework for Creating a Smart City Through Internet of Things, Padova Smart City: an Urban Internet of Things Experimentation, A Generic IoT Architecture for Smart Cities, ClouT: Cloud of Things for Empowering the Citizen Clout in Smart Cities.)} This urban "IoT" will enable a myriad of services and applications for the smart city, such as structural health monitoring, waste management, air quality monitoring, noise monitoring, traffic congestion avoidance, city energy consumption tracking, smart parking, smart lighting, charging infrastructure for electrical vehicles, creation of bike lane network to promote emission-free transport, city-wide wiring and sensorization for environmental data collection, etc. \refs{(Global Perspective of Smart Cities: A Survey, 2013, Smart City and the Applications).}}

@@

\rev{The use of LEDs lamps in street lighting started to be reported in the last few years, and it is being considered a very good solution to improve the energy efficiency of the system and also to reduce the maintenance cost \sout{replace the HID-based lighting systems}, because of their longer lifetime, higher luminous efficiency in mesopic visual conditions, and higher color rendering index (CRI) \citep{CRI_2008,CRI_2010}.} \sout{Also, LED lamps may also be dimmed to reduce its power consumption.
Therefore, the presence of LED lamps in the modern street lighting systems brings a need for better management, in order to decrease the maintenance cost and power consumption (e.g.: by lamp dimming).} \rev{Also, the addition of communication capability to the SLS decreases the energy consumption and the maintenance cost, because it allows for monitoring the status information of each lamp (state, current, voltage and power measurements, etc.) and to have better control of the system (e.g.: lamp dimming). \sout{If the system is connected to a network, the lamp power can be monitored and the luminary can be quickly replaced when a failure occurs, because a decrease of active power consumption is observed. Not only a preventive maintenance of the system can be easily programmed, but also software updates can be done (which allows future enhancements and addition of new functions).}  \sout{Then, a street lighting system with communication capability is justified by its advantages.} Then, a smart SLS, based on LED lamps and a communication network, is an interesting application in a smart city context, not only by its clearly advantages but also because it can be one of the foundations for a urban "IoT" due to its pervasiveness across the city \refs{(Smart Lighting solutions for Smart Cities)}. Therefore, it can also be an enabler for the aforementioned applications in the smart city.}

>>>>

\rev{With  the increase in world population and the growing urbanization worldwide, cities will need to evolve towards an intelligent infrastructure in order to provide to its citizens a better living environment. This will be achieved through the use of information and communication technology (ICT), with the goal to provide public services that are more accessible and more efficient. This vision is embodied in the ``smart city'' concept. \refs{(A Smart City and the Applications, 2011, Global Perspective of Smart Cities: A Survey, 2013).}}

\rev{According to several researchers, to enable the smart city it will be required an urban ``Internet of Things(IoT)'' infrastructure, where sensors and actuators distributed across the city will be interconnected by a pervasive network. \refs{(Developing an IoT Smart City Framework, Internet of Things for Smart Cities, An Information Framework for Creating a Smart City Through Internet of Things, Padova Smart City: an Urban Internet of Things Experimentation, A Generic IoT Architecture for Smart Cities, ClouT: Cloud of Things for Empowering the Citizen Clout in Smart Cities.)} This urban ``IoT'' will enable a myriad of services and applications for the smart city, such as structural health monitoring, waste management, air quality monitoring, noise monitoring, traffic congestion avoidance, city energy consumption tracking, smart parking, smart lighting, charging infrastructure for electrical vehicles, creation of bike lane network to promote emission-free transport, city-wide wiring and sensorization for environmental data collection, etc. \refs{(Global Perspective of Smart Cities: A Survey, 2013, Smart City and the Applications).}}

@@

\rev{The use of LEDs lamps in street lighting started to be reported in the last few years, and it is being considered a very good solution to improve the energy efficiency of the system and also to reduce the maintenance cost \sout{replace the HID-based lighting systems}, because of their longer lifetime, higher luminous efficiency in mesopic visual conditions, and higher color rendering index (CRI) \citep{CRI_2008,CRI_2010}.} \sout{Also, LED lamps may also be dimmed to reduce its power consumption.
Therefore, the presence of LED lamps in the modern street lighting systems brings a need for better management, in order to decrease the maintenance cost and power consumption (e.g.: by lamp dimming).} \rev{Also, the addition of communication capability to the SLS decreases the energy consumption and the maintenance cost, because it allows for monitoring the status information of each lamp (state, current, voltage and power measurements, etc.) and to have better control of the system (e.g.: lamp dimming). \sout{If the system is connected to a network, the lamp power can be monitored and the luminary can be quickly replaced when a failure occurs, because a decrease of active power consumption is observed. Not only a preventive maintenance of the system can be easily programmed, but also software updates can be done (which allows future enhancements and addition of new functions).}  \sout{Then, a street lighting system with communication capability is justified by its advantages.} Then, a smart SLS, based on LED lamps and a communication network, is an interesting application in a smart city context, not only by its clearly advantages but also because it can be one of the foundations for a urban ``IoT'' due to its pervasiveness across the city \refs{(Smart Lighting solutions for Smart Cities)}. Therefore, it can also be an enabler for the aforementioned applications in the smart city.}
